### 2014-03-02 paper/intro.tex
Abstract
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Information flow control (IFC) is a promising technique to enforce
security policies by tracking the flow of sensitive data through
a system.  The idea is to prevent the leaking of secret or sensitive
data into public channels by enforcing the notion of non-interference.
Significant research has been devoted to adding various
forms of IFC to different kinds of programming languages and system,
both static and dynamic in nature.  In this paper we are interested
in the latter, where an execution monitor ensure at runtime that secret
information is not revealed through public outputs.
A key challenge in the design of these dynamic systems has been the
performance cost incurred by additional security checks.
Particularly when retrofitting an existing programming language with
IFC it is tempting to track information flow at a fine-grained level,
e.g., per value in the system.  This can lead to impractical
runtime overheads even for ordinary operations.

>>>>

\Red{
    \begin{itemize}
        \item Complex software systems are composed of modules of different provenance
        \item Web applications have profilerated..components reuse libraries but also network accessible components
        \item IFC is a promising approach to preserving confidentiality
        \item Covert channels arise when programming features are misused to leak information
    \end{itemize}

Information flow control (IFC) has been shown to be useful in a variety
of settings, with applicability to web applications~\tocite{}, operating systems~\tocite{},
machine architectures~\tocite{}, and other contexts.  To this end, signifant research
has been devoted to adding IFC to various programming languages and systems.
}

Information flow control (IFC) is a promising technique to enforce
security policies by tracking the flow of sensitive data through
a system.  The usual policy one enforces prevent the leaking of secret or sensitive
data into public channels by enforcing the notion of non-interference.
Significant research has been devoted to adding various
forms of IFC to different kinds of programming languages and system,
both static and dynamic in nature.  In this paper we are interested
in the latter, where an execution monitor ensure at runtime that secret
information is not revealed through public outputs.
A key challenge in the design of these dynamic systems has been the
performance cost incurred by additional security checks.
Particularly when retrofitting an existing programming language with
IFC it is tempting to track information flow at a fine-grained level,
e.g., per value in the system.  This can lead to impractical
runtime overheads even for ordinary operations.
